How to improve your relationship with your future self.

### 2016-06-09 workflow.Rmd
Update workflow.Rmd

---
title: How to improve your relationship with your future self.
author:
- name: Jake Bowers
  affiliation: <jwbowers@illinois.edu>, University of Illinois at Urbana-Champaign, Departments of Political Science and Statistics; Fellow, White House Social and Behavioral Sciences Team. Many thanks to Mark Fredrickson, Brian Gaines, Kieran Healy, Kevin Quinn and Cara Wong for direct help on this document and to Mika LaVaque-Manty and Ben Hansen for many useful discussions on this topic. The source code for this document may be freely downloaded and modified from <https://github.com/jwbowers/workflow>.
- name: Maarten Voors
  affiliation: <maarten.voors@wur.nl>, Wageningen University, Development Economics
bibliography: references.bib
csl: american-political-science-review.csl
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
    pdf_document:
      keep_tex: true
      number_sections: true
      fig_width: 7
      fig_height: 7
      fig_caption: true
      template: bowersarticletemplate.latex
      pandoc_args: [
      "-M", "secPrefix=\\S",
      "--filter", "/usr/local/bin/pandoc-crossref"
      ]
      md_extensions: +autolink_bare_uris+ascii_identifiers+tex_math_single_backslash
...

@@

Moreover, realize that *file names send messages* to your future
self. This means that if you name your files with evocative and descriptive names, your
collaborators are less likely to call you at midnight asking for help and you will remove some regret from your future self. For example, if you are studying inequalit and protest, you might try naming a file something like  `inequality-and-protest-figures.R` instead of  `temp9`or
`supercalifragilisticexpialidocious`.  By the way, the extension
`.R` tells us and the operating system that the file contains R
commands. This part of the filename enables us to quickly search our
antique hard drives for files containing R scripts.

>>>>

---
title: How to improve your relationship with your future self.
author:
- name: Jake Bowers
  affiliation: <jwbowers@illinois.edu>,  University of Illinois at Urbana-Champaign, Departments of Political Science and Statistics; Fellow, White House Social and Behavioral Sciences Team. Many thanks to Mark Fredrickson, Brian Gaines, Kieran Healy, Kevin Quinn and Cara Wong for direct help on this document and to Mika LaVaque-Manty and Ben Hansen for many useful discussions on this topic. The source code for this document may be freely downloaded and modified from <https://github.com/jwbowers/workflow>.
- name: Maarten Voors
  affiliation: <maarten.voors@wur.nl>, Wageningen University, Development Economics Group
bibliography: references.bib
csl: american-political-science-review.csl
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
    pdf_document:
      keep_tex: true
      number_sections: true
      fig_width: 7
      fig_height: 7
      fig_caption: true
      template: bowersarticletemplate.latex
      pandoc_args: [
      "-M", "secPrefix=\\S",
      "--filter", "/usr/local/bin/pandoc-crossref"
      ]
      md_extensions: +autolink_bare_uris+ascii_identifiers+tex_math_single_backslash
...

@@

Moreover, realize that *file names send messages* to your future
self. This means that if you name your files with evocative and descriptive names, your
collaborators are less likely to call you at midnight asking for help and you will remove some regret from your future self. For example, if you are studying inequality and protest, you might try naming a file something like  `inequality-and-protest-figures.R` instead of  `temp9`or
`supercalifragilisticexpialidocious`.  By the way, the extension
`.R` tells us and the operating system that the file contains R
commands. This part of the filename enables us to quickly search our
antique hard drives for files containing R scripts.
